Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-01 paper.tex
Add fig and description for 3-D vorticity contours

>>>>

Visualizing the complicated wake generated by the turbine is presented for the
3-D Spalart--Allmaras case in Figure~\ref{fig:vorticity-3D}. It can be seen how
the upstream blade is shedding a large amount of spanwise vorticity due to the
separated flow. Strong tip vortices are also present, which trace the
``contracting'' wake flow on the $-y$ side of the turbine associated with the
induced vertical velocity field.

\begin{figure}
    \caption{Iso-vorticity contours colored by the streamwise component of
        vorticity for the 3-D Spalart--Allmaras case.}

    \label{fig:vorticity-3D}
\end{figure}
